figures?

### 2024-02-02 Updates/2023-11-17 figures_draft.Rmd
drafts

# Open dataset-------------
# start with lake temperatures
temperature_scores <- arrow::open_dataset("../scores_rescored") |>
  filter(site_id %in% lake_sites,
         # model_id != 'climatology',
         model_id %in% model_meta$model_id,
         variable == 'temperature') |>
  collect()

# Calculate skill scores ------------
temperature_climatology <- arrow::open_dataset("../scores_rescored") |>
  filter(model_id == 'climatology', 
         site_id %in% lake_sites,
         variable == 'temperature') |>
  collect() |> 
  select(reference_datetime, datetime, crps, logs, site_id, model_id) |> 
  arrange(reference_datetime, datetime, site_id) |> 
  pivot_wider(values_from = c(crps, logs),
              names_from = model_id)

@@

  # calcaulte the skill relative to climatology (- is bad, + is good)
  mutate(skill_crps = crps_climatology - crps,
         skill_logs = logs_climatology - logs,
         horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) |> 
  # consistent forecast period
  filter(horizon <= 30,
         horizon >= 1,
         model_id != 'fARIMA') |> 
  arrange(reference_datetime, site_id, datetime, model_id) 
```

@@

```{r}
NOAA_scores <- arrow::open_dataset("../scores") |>
  filter(site_id %in% lake_sites,
         model_id %in% c('NOAA_daily', 'NOAA_daily_obs')) |>
  collect()

@@

good_80 <- 
  plot_reliability(scores = temperature_scores,
                            models = top_mods$model_id, 
                            CI = 80, 
                            order = levels(top_mods$model_id)) +
  scale_color_brewer(name = 'Model', palette = 'Paired') +
  theme_bw() +
  scale_y_continuous(limits = c(45, 100))

good_95 <- plot_reliability(scores = temperature_scores,
                            models = top_mods$model_id, 
                            CI = 95, 
                            order = levels(top_mods$model_id)) +
  scale_color_brewer(name = 'Model', palette = 'Paired') +
  theme_bw() +
  scale_y_continuous(limits = c(45, 100))

@@

bad_80 <- 
  plot_reliability(scores = temperature_scores,
                   models = bad_mods, 
                   CI = 80, 
                   order = bad_mods) +
  scale_colour_discrete(name = 'Model') +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

bad_95 <- plot_reliability(scores = temperature_scores,
                            models = bad_mods, 
                            CI = 95, 
                            order = bad_mods) +
  scale_colour_discrete(name = 'Model') +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

ggarrange(ggarrange(good_80, good_95, bad_80, bad_95, align = 'hv', legend= 'none'), nrow = 2, align = 'hv') |> 
  ggsave(filename = 'Plots/Figure5.png', height = 25, width = 18, units = 'cm')
```

>>>>

# Open dataset-------------
# start with lake temperatures
temperature_scores <- arrow::open_dataset("../scores_2023") |>
  filter(site_id %in% lake_sites,
         model_id %in% model_meta$model_id,
         variable == 'temperature') |>
  collect()

# Calculate skill scores ------------
temperature_climatology <- arrow::open_dataset("../scores_2023") |>
  filter(model_id == 'climatology', 
         site_id %in% lake_sites,
         variable == 'temperature') |>
  collect() |> 
  select(reference_datetime, datetime, crps, logs, site_id, model_id) |> 
  arrange(reference_datetime, datetime, site_id) |> 
  pivot_wider(values_from = c(crps, logs),
              names_from = model_id)

@@

  # calcaulte the skill relative to climatology (- is bad, + is good)
  mutate(skill_crps = crps_climatology - crps,
         skill_logs = logs_climatology - logs,
         horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) |> 
  # consistent forecast period
  filter(horizon <= 30,
         horizon >= 1, 
         horizon != 15) |> 
  arrange(reference_datetime, site_id, datetime, model_id) 
```

@@

```{r eval = F}
NOAA_scores <- arrow::open_dataset("../scores") |>
  filter(site_id %in% lake_sites,
         model_id %in% c('NOAA_daily', 'NOAA_daily_obs')) |>
  collect()

@@

good_80 <- 
  plot_reliability(scores = temperature_scores,
                            models = top_mods$model_id, 
                            CI = 80, 
                            order = levels(top_mods$model_id)) +
  scale_color_brewer(name = 'Top Models', palette = 'Paired') +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

good_95 <- plot_reliability(scores = temperature_scores,
                            models = top_mods$model_id, 
                            CI = 95, 
                            order = levels(top_mods$model_id)) +
  scale_color_brewer(name = 'Top Models', palette = 'Paired') +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

@@

bad_80 <- 
  plot_reliability(scores = temperature_scores,
                   models = bad_mods, 
                   CI = 80, 
                   order = bad_mods) +
  theme_bw() +
  scale_colour_discrete(name = '') +
  scale_y_continuous(limits = c(0, 100)) + 
  theme(legend.position = 'bottom') + 
  guides(colour = guide_legend(nrow = 5))

bad_95 <- plot_reliability(scores = temperature_scores,
                            models = bad_mods, 
                            CI = 95, 
                            order = bad_mods) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 100))

ggarrange(ggarrange(ggarrange(get_legend(good_80), NULL, nrow = 2),
          ggarrange(good_80, good_95, bad_80, bad_95, align = 'hv', legend= 'none'), ncol = 2, 
          widths = c(1,5)),
          ggarrange(NULL, get_legend(bad_80), ncol = 2, widths = c(1,5)),
          ncol = 1, heights = c(5, 1)) |> 
  ggsave(filename = 'Plots/Figure5.png', height = 17.6, width = 22, units = 'cm')
```
